Kindly Bent to Free Us

### 2019-07-04 kindly/lang.tex
Fix typos.
Move Typing stuff around.

\subsubsection{Constraint language}

\newcommand\A{\mathcal A}
\newcommand\SC{\mathcal S}

Let us note $\A$ our constraint system. The grammar of constraints is
given in  \cref{grammar:constraint}.
$\A$ is defined as the smallest cylindric term constraint system that
satisfies the axiom shown in \cref{rules:entail}.
We follows the traditional HM(X) formulation
with conjunctions, projections and type inequalities.
The new element specific to our approach are kind inequalities.
Entailment is noted $\entail{C}{D}$, where $D$ is a consequence of the
constraints $C$.
We say that $C$ and $D$ are equivalent, noted $C \equivC D$,
when $\entail{C}{D}$ and $\entail{D}{C}$.
\TODO{Give the cylindric properties ?}

\begin{figure}[tp]
  \centering
  \begin{align*}
    C &::= \Cleq{\tau_1}{\tau_2}
        \mid \Cleq{k_1}{k_2}
        \mid C_1 \Cand C_2
        \mid \Cproj{\tvar}{C}
        \mid \Cproj{\kvar}{C}
  \end{align*}
  \caption{The constraint language}
  \label{grammar:constraint}
\end{figure}

\begin{figure*}[tp]
  \input{infer/lattice}
  \caption{Lattice inequalities -- $k \lk_\Lat k'$}
  \input{infer/entails}
  \caption{Base entailment rules -- $\entail{C}{D}$ }
  \label{rules:entail}
\end{figure*}

We note $\SC$ the set of solved forms
which can be used inside type and kind schemes.
We define $\SC$ as $\A$ quotiented by the relation $\equivC$.
%
We consider the existence of a function $\operatorname{normalize}$ which takes
a constraint in $\A$ and a substitution $\psi$ and returns a constraint
in solved form $C' \in \SC$,
and an updated substitution. We detail the implementation
of the normalization function in \cref{sec:normalize}

% $\mathcal S$ is composed only of kind
% inequalities \emph{over variables}. For convenience, if $C\in\mathcal S$, we
% note $C$ as a list of kind inequalities: $\Cleq{\kvar_i}{\kvar_{i'}}^n$.
% \TODO{Extend the properties of solved forms}

\subsubsection{Kinding}

We note $\inferSK{C}{\E}{\tau}{k}$
when $\tau$ has kind $k$ in environment $\E$ under constraints $C$.
The rules are shown in \cref{rules:sd-kinding}.
Kinds and types follow a small calculus with variables ($\tvar$,\dots),
functions (type constructors $\T{t}$), application ($\tapp{t}{\Multi{\tau}}$)
and primitives such as arrow ($\tau\tarr{k}\tau'$) and
borrow ($\borrowty{k}{\tau}$).
Kind inference is thus fairly straightforward and is done simply by following
the syntax of the types. The only kind arrows can appear when looking
up the kind scheme of a type constructor $\T t$. Kind arrows are forbidden
in any other contexts.

\begin{figure}[ht]
  \centering
  \input{infer/sd-kinds}
  \caption{Syntax-directed kinding rule --
    $\inferSK{C}{\E}{\tau}{k}$}
  \label{rules:sd-kinding}
\end{figure}

\subsubsection{Environments}

\begin{figure}[tp]
  \input{infer/sd-splitting}
  \caption{Splitting --- environments $\lsplit
    C\E\E\E$; binders $\bsplit Cbbb$}
  \label{fig:sd-splitting}
\end{figure}

\begin{figure}[tp]
  \input{infer/sd-borrowing}
  \caption{Borrowing --- environments $\lsplit
    C\E\E\E$; binders $\bsplit Cbbb$}
  \label{fig:sd-borrowing}
\end{figure}

\subsubsection{Typing}

\begin{figure*}[tp]
  \input{infer/sd-environments}
  \caption{Rewriting constraints on environments and types}
  \label{fig:contraints-environments-types}
\end{figure*}
\begin{figure*}[tp]
  \input{infer/sd-typing}
  \caption{Syntax-directed typing rules}
  \label{fig:syntax-directed-typing}
\end{figure*}

@@

\begin{figure*}[htp]
  \centering
  \input{region-annot}
  \caption{Automatic region annotation --- $\RannotT{e}{e'}$}
  \label{fig:region-annotation}
\end{figure*}

>>>>

\subsubsection{Bindings and Weakening}

\subsubsection{Regions and Borrows}

\begin{figure}
  \centering
  \begin{subfigure}{0.4\linewidth}
    \begin{mathpar}
      \ruleSDRegion
    \end{mathpar}
    \caption{The {\sc Region} rule}
  \end{subfigure}\hfill
  \begin{subfigure}{0.6\linewidth}
    \centering
    \begin{tabular}
      {@{}>{$}r<{$}@{ $\Lleftarrow$ }
      >{$}c<{$}@{ $\rightsquigarrow_n^{x}$ }
      >{$}l<{$}
      r}

      {(\kun_n\lk k\lk\kun_\infty)}
      &{\svar[\IBORROW]{x}{\tau}^n}
      &{\bvar{\borrow[\IBORROW]{x}}{\borrowty[\IBORROW] k{\tau}}}
      &Immut\\

      (\kaff_n\lk k\lk\kaff_\infty)
      &\svar[\MBORROW]{x}{\tau}^n
      &\bvar{\borrow[\MBORROW]{x}}{\borrowty[\MBORROW] k{\tau}}
      &Mut
    \end{tabular}
    \caption{Borrowing rules for bindings}
  \end{subfigure}
\end{figure}

\subsubsection{Copying and Splitting}

\begin{figure}
  \centering
  \begin{subfigure}{0.35\linewidth}
    \begin{mathpar}
      \ruleSDPair
    \end{mathpar}
    \caption{The {\sc Pair} rule}
  \end{subfigure}\hfill
  \begin{subfigure}{0.6\linewidth}
    \centering
    \begin{tabular}
      {@{}>{$}r<{$}@{ $\Lleftarrow$ }
      >{$}c<{$}@{ $=$ }
      >{$}c<{$}@{ $\ltimes$ }
      >{$}c<{$}r}

      \Cleq{\schm}{\kun_\infty}
      &\bvar{x}{\schm}&\bvar{x}{\schm}&\bvar{x}{\schm}
      &Both\\[2mm]

      {\Cempty}&{\bvar{x}{\schm}}&{\bvar{x}{\schm}}&{\bnone}
      &Left\\
      {\Cempty}&{\bvar{x}{\schm}}&{\bnone}&{\bvar{x}{\schm}}
      &Right\\[2mm]

      {\Cempty}&{\bvar x \schm}&{\svar x \schm^n}&{\bvar x \schm}
      &Susp\\

      {\Cempty}&
      {\bvar{\borrow x} \schm}&{\svar[\IBORROW] x \schm^n}&{\bvar{\borrow x} \schm}
      &SuspB\\[2mm]

      {\Cempty}&
      {\bvar{\borrow[i]{x}}{\schm}}&
      {\bvar{\borrow[i]{x}}{\schm}}&{\bvar{\borrow[i]{x}}{\schm}}
      &Borrow\\

    \end{tabular}
    \caption{Splitting rules for bindings}
  \end{subfigure}
\end{figure}

\subsubsection{Constraints}

@@

\begin{figure*}[!hbt]
  \centering
  \input{region-annot}
  \caption{Automatic region annotation --- $\RannotT{e}{e'}$}
  \label{fig:region-annotation}
\end{figure*}
